---
title: "Prediction"
output: html_document
---
## Summary


## Data source 

You can download the training [data](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv).

The test [data](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv).



## Exploraty Analysis
 
```{r}
# Load the libraries that we need 
library(caret)
library(rpart)
library(ggplot2)
library(rpart.plot)
library(rattle)
library(randomForest)
library(corrplot)
set.seed(1234)  # the random sequence 

# datasets

training <- read.csv("pml-training.csv")
testing  <- read.csv("pml-testing.csv")

# create a partition with the training dataset 
inTrain  <- createDataPartition(training$classe, p=0.7, list=FALSE)
TrainSet <- training[inTrain, ]
TestSet  <- training[-inTrain, ]
```

# Cleaning the data

```{r}
# Remove variables with Nearly Zero Variance
NZV <- nearZeroVar(TrainSet)
TrainSet <- TrainSet[, -NZV]
TestSet  <- TestSet[, -NZV]

# remove variables that are mostly NA
AllNA    <- sapply(TrainSet, function(x) mean(is.na(x))) > 0.95
TrainSet <- TrainSet[, AllNA==FALSE]
TestSet  <- TestSet[, AllNA==FALSE]

# remove identification only variables (columns 1 to 5)
TrainSet <- TrainSet[, -(1:5)]
TestSet  <- TestSet[, -(1:5)]

# Data Training 
print(dim(TrainSet))
# Data Test
print(dim(TestSet))
```

# Correlation 

```{r}
corMatrix <- cor(TrainSet[, -54])
corrplot(corMatrix, order = "FPC", method = "color", type = "lower", 
         tl.cex = 0.8, tl.col = rgb(0, 0, 0))
```
The highly correlated variables are shown in dark colors in the graph above. Their colors are either dark blue (for a positive correlation) or dark red (for a negative correlations) 


# Prediction Model

## Decision Tree Model
```{r}
fit_decision_tree <- rpart(classe ~ ., data = TrainSet, method="class")
fancyRpartPlot(fit_decision_tree)

```
Predictions of the decision tree model on TestSet.

```{r}

predict_decision_tree <- predict(fit_decision_tree, newdata = TestSet, type="class")
conf_matrix_decision_tree <- confusionMatrix(predict_decision_tree, TestSet$classe)

conf_matrix_decision_tree
```


# Correlation 

```{r}


```

# Correlation 

```{r}


```

# Correlation 

```{r}


```
